---
title: "Isaac Madland - Capstone Presentation"
subtitle: "Physiotherapist or Carpenter"
author: "Isaac Madland"
institute: "Mount Boucherie High School"
date: "2026-05-14"
format:
  revealjs:
    multiplex: true
    incremental: true
    theme: default
  pptx: default
# bibliography: refs.bib
# csl: .apa.csl
# logo: otessa-logo-CS6.png
footer: "imadland@icloud.com" 
freeze: false
toc: false
draft: true
---

```{r}
library(gt)
```

## My Learning Story

- Football & Rugby
- Injuries
  - concussions
  - meniscus
  - ACL

---

## My Learning Story

- Post-concussion Syndrome
  - migraines
  - brain fog
  - difficulty with concentrating


---


## My Learning Story

- Triggers
  - flourescent lights
  - projectors
  - hallway noise

---


## My Learning Story

- Human Kinetics
  - interest in injury recovery
  - desire to stay connected with organized athletics

---


## My Learning Story

- Grandpa Gore Award
  - determination
  - faith in teammates
  - leadership

---

## Core Competency

### Critical Thinking

- challenging due to PCS
- significant difficulty with math and science in Gr 9-10
- turnaround in Math 10 (thank you Ms...!)

---

### Critical Thinking

- personal sense of pride
- exceeded my own expectations

---

## Skills Showcase

### Music

### Athletics


---

## Skills Showcase - Music

- drumming since age 4
- older brother was an inspiration
- impeccable sense of timing
- offered session gigs from producers

---

## Skills Showcase - Music

- have already connected with musicians near TWU
- plan to get involved as much as possible

---

## Plan A - Physiotherapy

- execute treatment plans
  - improve physical ability
  - ease pain
  - prevent further problems

---

## Plan A - Physiotherapy

- need to manage complex needs with every patient (e.g. torn biceps brachii vs plantar fasciitis)
- requires deep knowledge of anatomy and physiology
- diagnoses from process of elimination

---

## Plan A - Physiotherapy

### Working Conditions

- wide variety
  - public clinics
  - private practice
  - hospitals
  - travelling to remote locations
- combination of office and gym environment

---

## Plan A - Physiotherapy{}

### Salary and Outlook

```{r}
salaries_tbl <- read.csv(file = "salaries.csv")

gt(salaries_tbl) |>
  tab_source_note(
    source_note = "Source: Indeed"
  ) |>
  cols_align(
    align = "center",
    columns = "Salary.per.year"
  ) |>
  cols_align(
    align = "right",
    columns = "Relation.to.Average"
  )
```

---

## Plan A - Physiotherapy

### Outlook

- average provincial need is moderate. 
- higher demand in the Maritimes and Alberta.

---

## Plan A - Physiotherapy

### Educational Pathways

- A masters degree in physiotherapy along with a period of supervised practical training
-  A license or registration with a regulatory body
- Completion of physiotherapy competency

---

## Plan A - Physiotherapy

### Educational Pathways

- BHK at Trinity Western University
- MSc at UBC

---

## Plan A - Physiotherapy

### Why Physio?

- athletics
- injuries
- recovery is physical and mental
- struggled with depression and anxiety
- desire to help people recover
- help people feel seen and respected

---

## Plan A Budget Overview

```{r}
budget_tbl <- read.csv(file = "budget.csv")

gt(budget_tbl) |>
  cols_align(
    align = "right",
    columns = "Amount"
  )
```


## Plan B - Carpentry

- wide variety of individual trades
- physically demanding
- requires skill with hand tools
- job sites vary, and are outside
- requires heavy lifting, use of dangerous tools, and PPE

---


## Plan B - Carpentry

### Educational Pathway

- high number of entry-level jobs
- many apprenticeship pathways allow students to work while going to school
- significant investment from Government of Canada in trades

---

## Plan B - Carpentry

### Why this plan B?

- love working with my hands
- many memories of working with my Grandpa
- easy to start, could start after high school
- $77,800 starting wage (Indeed)
- flexibility

---

## Work/Volunteer (Mentor) Experience

- XX hours
- documentation is submitted




